Cluster Difference Imaging Photometric Survey. III. An Open Cluster With a 300\,pc Halo

### 2021-02-19 cluster_paper/ms.tex
update paper

Figure~\ref{fig:rot} shows the resulting rotation periods.  The points
on this plot are the \nautorotnumerator light curves for which the peak Lomb Scargle
periodogram period was below 15 days, the LS power exceeded 0.08, and
for which no equal-brightness or greater companions were within the aperture. 
We also required that at most one companion with brightness exceeding 
one tenth of the target star could reside in the aperture.
These
selection criteria are entirely heuristic, and yielded
\nautorotdenominator stars for which rotation periods might have been
detected.  
By exploring the different possible selection criteria, we found that
the ones we chose provided a
reasonable balance between excluding stars on the slow sequence, {\it
vs.} reporting spurious rotation periods in the ``void'' below the
slow sequence, where the dominant signal was in fact from a
neighboring star.
Splitting the resulting sample into the ``core'' and the ``halo'', they
suggest that the halo is real.

The resulting gyrochronology age we find for the core is XXX.
For the halo, the claimed age from gyrochronology is YYY.
Applying the same procedure to the field star comparison sample,
we get an age of ZZZ.

\subsubsection{Comparison Star Sample}

@@

>>>>

Figure~\ref{fig:rot} shows the resulting rotation periods.  The points
on this plot are the \nautorotnumerator light curves for which the peak Lomb Scargle
periodogram period was below 15 days, the LS power exceeded 0.08, and
for which no equal-brightness or greater companions were within the aperture. 
We also required that at most one companion with brightness exceeding 
one tenth of the target star could reside in the aperture.
These
selection criteria are entirely heuristic, and yielded
\nautorotdenominator stars for which rotation periods might have been
detected.  
By exploring the different possible selection criteria, we found that
the ones we adopted provided a
reasonable balance between excluding stars on the slow sequence, {\it
vs.} reporting spurious rotation periods in the ``void'' below the
slow sequence, where the dominant signal was in fact from a
neighboring star.
Splitting the resulting sample into the ``core'' and the ``halo'', they
suggest that the halo is real.

To put the clusters on the same color scale, we needed to adopt
reddening corrections.
We assumed {X} for the Pleiades, and {Y} for Praesepe.
For NGC\,2516, we queried the 2MASS DUST service to find the
extinction parameters for the positions of each NGC\,2516 member
(CITE: astrobase.services.dust; 2MASS DUST).  The mean and standard
deviation of the E(B-V) values for the Schlegel+98 and SF11 maps were
consistent, so we considered those of Schlegel+1998:
$E(B-V)=0.206\pm0.039$.  Bonifacio+2000 noted though that Schlegel+98
overestimate the reddening values when the color excess exceeds about
0.10 mag. We applied their correction (Eq 1 from Bonifacio+2000),
which led to an adopted $E(B-V)=0.102\pm0.019$.  Finally, to convert
to Gaia colors we adopted the calibration of Stassun et al 2019, and
assumed $E(Bp-Rp)=1.31 E(B-V)$ and $A_G=2.72 E(B-V)$.  This yielded
$E(Bp-Rp)=0.134\pm0.025$, which is used in the plots.

The resulting gyrochronology age we find for the core is XXX.
For the halo, the claimed age from gyrochronology is YYY.
Applying the same procedure to the field star comparison sample (see
Appendix~\ref{app:compstar}),
we get an age of ZZZ+/-AAA.

@@

\section{Comparison Star Rotation Periods}
\label{app:compstar}
